---
title: "Mapping data to graphics"
subtitle: "Exercise 3 --- PMAP 8551, Fall 2024"
author: "YOUR NAME HERE"
date: "DATE GOES HERE"
date-format: "long"
format:
  html:
    toc: true
  pdf:
    toc: true
  docx:
    toc: true
---

---

# Task 1: Reflection

Put your reflection here


# Task 2: Lord of the Rings

## Load and clean data

First we load, restructure, and clean the data.

```{r}
#| label: load-clean-data
#| warning: false
#| message: false

# You'll only need the tidyverse library for this exercise
library(tidyverse)

# Load the separate datasets
fellowship <- read_csv("data/The_Fellowship_Of_The_Ring.csv")
tt <- read_csv("data/The_Two_Towers.csv")
rotk <- read_csv("data/The_Return_Of_The_King.csv")

# bind_rows() stacks data frames on top of each other
lotr_wide <- bind_rows(fellowship, tt, rotk) |> 
  # Make the Film column a categorical variable (factor), and put it in the
  # order the categories appear (so the films are in the correct order)
  mutate(Film = fct_inorder(Film))

# Make this wide data tidy
lotr <- lotr_wide |> 
  # This is the new way to make data long
  pivot_longer(cols = c(Female, Male), 
               names_to = "Gender", values_to = "Words")
```


## Species

Does a certain species dominate (i.e. speak the most) the entire trilogy? (hint: group by `Species`)

```{r}
# Do stuff here
```


## Gender and film

Does a certain gender dominate a movie? (lolz of course it does, but still, graph it) (Hint: group by both `Gender` and `Film`.) Experiment with filling by `Gender` or `Film` and faceting by `Gender` or `Film`.

```{r}
# Do stuff here
```


## Species and film

Does the dominant species differ across the three movies? (Hint: group by both `Species` and `Film`.) Experiment with filling by `Species` or `Film` and faceting by `Species` or `Film`.

```{r}
# Do stuff here
```


## Species and gender and film

Create a plot that visualizes the number of words spoken by species, gender, and film simultaneously. Use the complete tidy `lotr` data frame. You don't need to create a new summarized dataset (with `group_by(Species, Gender, Film)`) because the original data already has a row for each of those (you could make a summarized dataset, but it would be identical to the full version).

You need to show `Species`, `Gender`, and `Film` at the same time, but you only have two possible aesthetics (`x` and `fill`), so you'll also need to facet by the third. Play around with different combinations (e.g. try `x = Species`, then `x = Film`) until you find one that tells the clearest story. For fun, add a `labs()` layer to add a title and subtitle and caption.

```{r}
# Do stuff here
```
